---
title: "Lab4ofDOOM"
author: "Eric Herwin and Albin Västerlund"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains one function of a class RC and the prime function for this is to calculate a linear regression. 

## The function, class and methods

The function and class, `linreg` and the function can take two arguments, `formula` and `data`. The function has serveral methods connected to it and if you refer to them they will do different tasks. Such as:

- `print()`: will print out the basic information about the linear regression, like how the Call function looks like and the coefficient and its estimations.
- `summary()`: will print out the same information as the `print()` method, but will include t-values, p-values, standard errors for parameters. It will also include the standard deviation for the model aswell.
- `resid()`: will print out the residuals of the model as a vector.
- `pred()`: will print out the predicted values of the model as a vector.
- `coef()`: will print out the coeficients estimations as a vector.
- `plot()`: this will plot the residuals vs. fitts and the standardized residuals vs fitts. The plots are generated with the package `ggplot2`. How these plots will look like are presented in the Plot chapter, little further down.

These methods need be "fed" with som information on what to do. The function `new(...)` can insert what you want in to the class. How to refer to this method for a RC class you need to use a `$` sign in the context of `linreg$new(formula, data)`. To refer to a methods that you have created, and to use the information you have put in to the `new(...)` function, you have to put in, for example `linreg$new(formula, data)$print()`. This will print out the information about the linear regression according to the `print()` method.


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
